\IEEEraisesectionheading{\section{Introduction}}
%\vspace{-2mm}
%\begin{CJK}{GBK}{song}
%\begin{CJK}{UTF8}{gkai}
%\ \ \ \ \ 侧信道攻击的危害及研究的必要
%攻击分类，有哪些攻击
%防御方法有哪些
%防御的问题：对算法本身进行修改，对硬件进行修改，可用性不强
%我们的研究：针对敌手需要的能力最弱的攻击，时间攻击
%提出一个防御框架
%保证了在AES计算时不泄露信息
%在安全的同时，计算效率最高
%
%\end{CJK}
    %Kocher1996Timing 对RSA和ECC的攻击，利用不同运算的计算时间
    %Tsunoo2003Cryptanalysis: 针对DES的攻击，first practical，time-driven attacks
    %Bernstein2005Cache 远程攻击，但是没有给出具体示例it is extremely difficult to load an array entry in time that does not depend on the entry's index. Is AES the only cryptographic function vulnerable to this type of attack? No. The relevant feature of AES software, namely its heavy reliance upon S-boxes, is shared by cryptographic software for many other functions（但举的例子不太明显）
    %Ac2006Trace：trace attack，所需要的trace数目较少
    %Bonneau2006Cache：基于lookup table的AES实现。common table-driven software implementation of the AES cipher，在此之前最优的攻击是Bernstein2005Cache，起将所学的明密文对数目降低了4个数量级 represent a significant step towards developing realistic remote timing attacks against AES,
    %Neve2006A 对Bernstein2005Cache的一个更细致的分析，指出其能成功的原因
    %Tsunoo2003Cryptanalysis First practical results for time-driven cache attacks on the Data Encryption Standard (DES)
    %Gullasch2011Cache access-driven attack, 近乎实时攻击，所需的样本量很少，非特权的spy进程，也是先学习，后猜测的过程。针对AES
    %Osvik2005Cache: evict+time，on AES
    %Tromer2010Efficient 是Osvik2005Cache的journal版本
\IEEEPARstart{I}{n}  practical cryptographic algorithm implementations,
   the cryptographic keys could be leaked through  side channels on
    timing \cite{Acii2005Improving,Ac2006Trace,Bonneau2006Cache,Bernstein2005Cache,Gullasch2011Cache,Kocher1996Timing,Neve2006A,Osvik2006Cache,Tsunoo2003Cryptanalysis,Tromer2010Efficient}, % 引用一些在不同的方法上，有开创性的
    electromagnetic fields \cite{Electromagnetic-sidechannel}, power \cite{power-pc,Bertoni2005AES},
 ground electric potential \cite{electric-potential-sidechannel} or acoustic emanations \cite{Acoustic-sidechannel},
  even when the algorithm is semantically secure.
%  Side channel attacks are using these vulnerabilities to obtain the sensitive information.
  Among these vulnerabilities,
   \emph{timing side-channel attacks} are launched easily without any special probe devices.
In particular, \emph{remote timing side channels} allow attackers, who have
    no system privilege or physical access to the computer,
    to discover the keys
    by repeatedly invoking the encryption/decryption functions and measuring the execution time \cite{Bernstein2005Cache,Bonneau2006Cache,Neve2006A,Brumley2011Remote,Brumley2005Remote}. % Tsunoo2002Cryptanalysis,
% 公钥算法的timing，也很明显，但是与cache无关？引用remote cache攻击
%Public key algorithms have proved the most vulnerable to timing attacks because they typically perform lengthy mathematical operations, the running time of which depends directly on the data due to branch statements
%Timing side channel attacks are the easiest to be carried out because the time is measured simply and they don't require specialized equipment.
%在AES选举的过程中，认为AES是基于查找表的实现，其是能够抵抗像RSA、ECC这些分支跳转产生的执行时间差异所引入的side channel attack

One type of remote timing side channels,  called \emph{remote cache timing side channels} in this paper, %passively
 exploits the time differences of data-cache hits and misses. Such cache timing side channels are widely found in the implementations of block ciphers \cite{Ac2007Cache,Bernstein2005Cache,Tsunoo2003Cryptanalysis,atici2016remote,saraswat2014remote}. % Brumley2011Remote,Brumley2005Remote, 分别是针对ECC 和RSA 的，而且不是针对cache hit or miss的。 广泛存在\cite{}
In the implementations,
  table lookup is the primary time-consuming operation in encryption/decryption.
The overall execution time %of block ciphers
 is influenced by the number of cache misses/hits in table lookup.
%Because accessing data in caches is much faster than those in RAM chips,
% cache hits and misses in table lookup
%    significantly influence the overall execution time of block ciphers.
Therefore,
   from the execution time, attackers are able to infer the inputs of table lookup operations which are determined by the secret keys (and the known plaintext/ciphertext).
Generally, for a block cipher,
  encryption and decryption are symmetric computations with same basic operations.
So  we only emphasize on encryption in the rest of the paper,
    but all discussions and conclusions are applicable to decryption.
%Different inputs of table lookup cause different cache access behavior so that the overall time differs, which are related to the secret keys,    and then the information about keys leaks.

%	Cache timing side channel是指利用密码计算过程中，对于cache/RAM访问而导致的timing特征，获得密钥。在大量的对称密码算法中，有“与key相关的查表操作”，与cache相关；影响到timing。攻击者就可以从timing获得推导密钥信息。
%	Remote side channel是指，攻击者可以远程发起，不需要接触或者近距离在密码系统旁边，也不需要在密码计算机器上有什么操作权限。相比其他的side channel，remote cache timing side channel的攻击条件很低，影响更多。最早是有……攻击[??]，后来又有什么发展。

%Remote timing cache side channels widely exists in the software implementations of cryptographic algorithms,
%  and are practical to be exploited~\cite{Ac2007Cache,atici2016remote,Bernstein2005Cache,saraswat2014remote}.
Compared with other side channels, such as
 power, electromagnetic fields,
 ground electric potential and acoustic emanations,
 cache-based timing side-channel attacks do not require special equipments
    or extra physical access to the victim system.
 Moreover,
  such remote attacks only require the least privilege to (remotely) invoke the encryption functions,
while other active cache-based side-channel attacks involve operations
 by a malicious task that shares caches with the victim cryptographic engine
%   such as cross-VM side-channel attack, FLUSH+RELOAD, and access-driven cache-attacks
\cite{YinqianZhang2012-cross-vm,get-off-my-cloud,flushreload,Gullasch2011Cache}.


%Since little acquirements are needed, this type attack is easy to deploy and hard to defense.
Various methods are proposed against cache timing side-channel attacks,
  destroying the relationship between the secret keys and the execution time.
The intuitive design is
    to perform encryption, \emph{a})  with the lookup tables completely inside or outside caches,
    or \emph{b}) in a constant period of time, regardless of cache utilization.
%Although the existing methods can offer some security guarantee, most of them have some drawbacks.
%It is difficult to perform a universal and high efficient method to defend against the remote cache timing attacks.
%In particular,
 {\scshape{Warm}} and  {\scshape{Delay}} are two typical algorithm-independent and implementation-transparent mechanisms
    to eliminate cache timing side channels \cite{Braun2015Robust,Osvik2006Cache,Zhang2011Predictive}.
    {\scshape{Warm}} fills cache lines by reading constant tables \emph{before} the encryption operations,
    and
    {\scshape{Delay}} inserts padding instructions \emph{after} encryption.\footnote{Another choice is to perform encryption without using caches, which is very inefficient.
     In fact, a typical strategy of {\scshape{Delay}}
     is to extend the encryption operation in constant time, equal to the execution time without caches.} With {\scshape{Warm}} or {\scshape{Delay}}, the execution time measured by attackers becomes \emph{irrelevant} to the cache misses/hits \emph{during} encryption.

These two common mechanisms prevent cache-based timing attacks at different phases,
    but they introduce extra operations and significantly degrade the performance. %especially in naive implementations.
In this paper, we investigate the performance of symmetric cryptographic functions that adopt {\scshape{Warm}} and {\scshape{Delay}} to defend against cache timing side channel attacks,
  and attempt to find \emph{the optimal strategy to integrate these two mechanisms} to achieve the optimized performance.
%    with the optimal performance while effectively eliminate remote cache side channels.
%As there are different strategies to apply {\scshape{Warm}} and  {\scshape{Delay}} in the implementations of block ciphers,
%% %Gullasch2011Cache 是说：1.将进程和data绑定，从而保证cache hit；2.将查找表uncacheable，每次cache miss
%Intro：
%	各种Side channel威胁到密码系统的安全性，包括timing、电磁、xxxx、xxx。利用Side channel攻击者能够获得密钥。Timing side channel是其中容易发起的一种，因为只需要计时、不需要专门的设备。
%	Cache timing side channel是指利用密码计算过程中，对于cache/RAM访问而导致的timing特征，获得密钥。在大量的对称密码算法中，有“与key相关的查表操作”，与cache相关；影响到timing。攻击者就可以从timing获得推导密钥信息。
%	Remote side channel是指，攻击者可以远程发起，不需要接触或者近距离在密码系统旁边，也不需要在密码计算机器上有什么操作权限。相比其他的side channel，remote cache timing side channel的攻击条件很低，影响更多。最早是有……攻击[??]，后来又有什么发展。
%    we attempt to integrate them into a scheme
%   achieving the optimal performance while effectively eliminating remote cache timing side channels.
The following principles are analyzed and discussed in the integration:
\begin{enumerate}
\item
%Each encryption is protected by {\scshape{Warm}} or {\scshape{Delay}},
%   i.e., it is performed with all lookup tables in caches
%   or it is finished with a constant period of time.
%%Destroy the relationship between the execution time and cache misses/hits,   to ensure security.
%The measured time reflects either the best case (i.e., all lookup tables are cached by {\scshape{Warm}}),
%     or the worst case (i.e., it is delayed to the execution time without any caches).
%      Otherwise the cache side channel attacks may be launched.
Each encryption is protected by {\scshape{Warm}} and/or {\scshape{Delay}},
so that the measured time reflects either the best case (i.e., all table entries are cached by {\scshape{Warm}}),
     or the worst case (i.e., it is delayed to the execution time without any caches).
      Otherwise, the cache timing side channel attacks may still be launched.

\item
In order to optimize the performance,
  {\scshape{Warm}} is preferred to {\scshape{Delay}};
  i.e.,
    finish  encryption operations as many as possible, with all table entries in caches.
%Note that,
%    compared with the best case protected by {\scshape{Warm}},
%  the worst case by {\scshape{Delay}} costs about eight times of CPU cycles.
Only when the effect of {\scshape{Warm}} is broken  by system activities, such as interrupts and task scheduling,
    i.e. the information on the secret key may be leaked,
  the execution time is delayed to the worst case.

\item
% 将warm放到delay的时间中
When {\scshape{Delay}} is performed,
  {\scshape{Warm}} is  done as a part of inserted padding instructions
   for the next encryption.
So, the cost of {\scshape{Warm}} is masked by padding instructions,
and the performance is further improved.
\end{enumerate}


%1. the时间与data无关，或者是全部都在cache的时间，或者是全部都不在cache的时间；使得无法推导data相关
%2. 优先使用warm；使得能够提高效率；注意：warm也是需要占用时间的。warm没有效果时，用delay。
%3. 条件的判断，基于时间，不需要特殊的操作和权限；

The integrated scheme does not require any privileged operation on computer systems.
The conditions to perform {\scshape{Warm}} and {\scshape{Delay}}, are defined as regular timing.
Reading constant tables, inserting padding instructions, and timing are commonly supported in computer systems
    without special privileges.
The scheme is independent of algorithms and transparent to implementations.
   It does not depend on any special design or feature of block ciphers,
and it is applicable to different implementations.
%  except that the lookup tables are accessible in the warm operations.

We apply the integrated {\scshape{Warm+Delay}} scheme to protect AES,
    and analyze the conditions that produce the optimal performance.
It is proven that,
   the integrated scheme with appropriate parameters,
   achieves \emph{the optimal performance with the least extra operations};
    that is, without any unnecessary lookup table read operations
   or inserted padding instructions.
%In particular, we apply this scheme to AES,
%It is found that,
The optimal performance of the integrated {\scshape{Warm+Delay}} scheme with different key sizes (128, 192, and 256 bits)
    and different implementations (2KB, 4KB, 4.25KB, and 5KB lookup tables),
    is investigated in commodity computers.
For example,
    the protected AES-128 implementation with a 2KB lookup table \cite{Daemen2002The} achieves the optimal performance,
\textcolor[rgb]{1.00,0.50,0.50}{when the ratio of
  the extra execution time caused by {\scshape{Delay}} to the extra execution time caused by {\scshape{Warm}},
  denoted as $G$, is less than $167.7$.}
These conditions hold %for continuous AES executions
 in commodity computers,
  which is confirmed by our experiments.
The conditions of the optimal performance for other AES implementations of different key sizes are not identical but also hold in commodity systems.
%In fact, our protection scheme produces the optimal performance for various AES implementations (the lookup tables in size of 2KB, 4KB, 4.25KB and 5KB) of different key sizes (128, 192 and 256 bits),


To the best of our knowledge,
  this is the first to systematically analyze the optimal performance of
    integrating {\scshape{Warm}} and {\scshape{Delay}} against cache timing side channels  in commodity systems.
Our contributions are as follows:
\begin{itemize}
\item
We investigate the overheads of {\scshape{Warm}} and {\scshape{Delay}},
    and derive the scheme to integrate these countermeasures
        with the optimal performance while effectively eliminate remote cache side channels.
%These countermeasures are algorithm-independent and implementation-transparent,
%   and do not require any privileged operation. % on the computer system.
%We apply the integration scheme to AES,
%   and analyze the detailed situations that it produces the optimal performance.

\item
We implement the optimal integration scheme on Linux with Intel CPUs for AES-128,
  and experimentally confirm that it (\emph{a}) eliminates cache timing side channels,
   (\emph{b}) outperforms other different integration strategies, % of {\scshape{Warm}} and {\scshape{Delay}},
    and
   (\emph{c}) works without any privileged operation on the system.




% 继承了基本操作的特性：算法无关、实现无关、平台无关。
% integration过程也是如此。
%%The two basic elements are integrated in the way that the {\scshape{Warm+Delay}} scheme
%%  is widely applicable. % to different algorithms, implementations and computing platforms.
%%{\scshape{Warm}} and {\scshape{Delay}} are independent of algorithms and implementations,   work on various computer systems.
%%%These features are kept in the integrated scheme,
%%%  which is applicable to various implementations with lookup tables of different block ciphers,
%%%     and does not require any privileged operation on the computer system.
\end{itemize}


%	已有的消除(Remote) Cache Timing Side Channels有各种各样，包括ABCDEFG。逐一大致说明。
%	已有方法的大致思路都是：……有一个总结【是什么？】这些方法为了避免攻击者从timing推导得到cache hit/missing 信息、进而推导得到key信息，都会使得timing (or speed)受到防御措施的影响，也就是速度降低。
%	本文提出了一种框架，to eliminate remote cache timing side channels, while保持最优性能。我们方法的基本思路是，结合warm和delay【这2个关键词，别人是这么用的吗？不要自己造出来一些term，要用已有的term来描述创新的方法/方案，别人才能够更好更快地理解】，……【说明我们的大致思想】
%	我们实现了方案，实验等等

The remainder of this paper is organized as follows.
Section \ref{sec:background} presents the background and related works.
Section \ref{sec:eliminating} discusses the {\scshape{Warm+Delay}} scheme and analyzes its security.
Section \ref{sec:performanceproof} proves the optimal integration scheme,
 which is verified in Section \ref{sec:implementationEvalution}.
Section \ref{sec:discussion} contains extended discussions.
Section \ref{sec:conclusion} draws the conclusions.
%Appendix \ref{appendixa} provides the proof of the optimized performance in details,
% while Appendix \ref{appendixb} analyzes various implementations of AES with different key lengths.
